---
title: Mixed Models Analysis and Data Visualization of Political Affiliation's Impact on Perception and Sentiment
output: html_notebook
---

```{r setup, include=FALSE}
# Load required libraries and data

if (!require("lme4")) install.packages("lme4")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("dplyr")) install.packages("dplyr")
if (!require("tidyr")) install.packages("tidyr")

library(lme4)
library(ggplot2)
library(dplyr)
library(tidyr)

data <- read.csv("data/strategic_signaling_data_long.csv")
```

# Mixed Models Analysis
```{r}
# Model for avg_perceived
model_perceived <- lmer(avg_perceived ~ poli_affil + (1|tweet), data = data)

# Model for avg_sentiment
model_sentiment <- lmer(avg_sentiment ~ poli_affil + (1|tweet), data = data)

# Summaries
summary(model_perceived)
summary(model_sentiment)
```

# Results Summary
The mixed models analysis suggests that political affiliation has a significant effect on both average perception (`avg_perceived`) and average sentiment (`avg_sentiment`).

### Key Findings:

The mixed models analysis suggests that political affiliation has a significant effect on both average perception (`avg_perceived`) and average sentiment (`avg_sentiment`).

#### - Average Perception (`avg_perceived`)

- Individuals with a "right" political affiliation tend to have a significantly higher average perception (0.43 units higher) compared to those with the reference political affiliation. 

#### - Average Sentiment (`avg_sentiment`)
- Individuals with a "right" political affiliation also show a significant increase in average sentiment (0.073 units higher) compared to those with the reference political affiliation.

# Bar Plot
```{r}
# Prepare data for the bar plot
plot_data <- data %>%
  group_by(poli_affil) %>%
    summarize(avg_perceived = mean(avg_perceived, na.rm = TRUE), avg_sentiment = mean(avg_sentiment, na.rm = TRUE))
 
# Convert data to long format for ggplot2
plot_data_long <- plot_data %>%
  pivot_longer(cols = c(avg_perceived, avg_sentiment), names_to = "measure", values_to = "value")

# Create the bar plot
ggplot(plot_data_long, aes(x = poli_affil, y = value, fill = poli_affil)) +
  geom_bar(stat = "identity", position = "dodge") +
    facet_wrap(~ measure, scales = "free_y") +
      labs(title = "Average Perceived and Sentiment by Political Affiliation", x = "Political Affiliation", y = "Average Value") +
        theme_minimal()
```